Fig2: Candidate genes

### 2020-04-18 analysis/figure-2.Rmd
first pass at new WGCNA

```{r writefiles}
#write.csv(candidatevsd, "../../musicalgenes/data/candidatecounts.csv")
#write.csv(candidatevsd, "../results/candidatecounts.csv")
write.csv(table1, "../results/table1.csv")
```

>>>>

```{r writefiles}
#write.csv(candidatevsd, "../../musicalgenes/data/candidatecounts.csv")
#write.csv(candidatevsd, "../results/candidatecounts.csv")
write.csv(table1, "../results/table1.csv")
write.csv(candidategenes, "../results/candidategenes.csv")
```
